\section{References}  % Note: the section heading 'References' will be automatically inserted, so delete this from your report
\label{sec:refs}

The reference list should be provided after the conclusion, and before any appendices (which are introduced with the \verb|\appendix| command). The reference list that appears below is marked up in \LaTeX\ as follows.

\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{Kopka2003} H~Kopka and F~W Daly. {\em Guide to \LaTeX}.
  Addison-Wesley, Boston, 4th edition, 2003.
\bibitem{Cmbr} Cosmic microwave background, Wikipedia.
  \url{http://en.wikipedia.org/wiki/Cosmic_microwave_background}.
  Accessed 1st Jan 2017.
\bibitem{Ashkin1986} A~Ashkin, J~M~Dziedzic, J~E~Bjorkholm, and S~Chu. 
  Observation of a single beam gradient force optical trap for
  dielectric particles.
  {\em Optics Letters}, 11:288--290, 1986.
\end{thebibliography}
\end{verbatim}

Each item in the list is labelled with a \verb|\bibitem{label}| command; it is this label that is used in \verb|\cite{label}| commands. In scientific writing, we prefer fixed, permanent references (such as books and journal articles) to webpages. The above shows the information to include for books, webpages and journal articles respectively: these will be the three most common reference types. The usual order to present the references in is the order in which they are cited in the main text.

Typing out all of these references in a consistent format, and getting the order right, can be a laborious task. A companion utility called Bib\TeX\ uses a database of references to automate this process, and is strongly recommended. In fact, the bibliography in this document was automatically generated in this way. See Appendix~\ref{sec:bibtex} for more information.

Note: since this template document is not an actual project report, we have embedded some clickable weblinks in the text for your convenience. This is \emph{not} the standard way to make citations in a piece of scientific writing, and you must not use this as an alternative to proper citations with the \verb|\cite| command. Note that if you use the \verb|hyperref| package (as here) proper citations will \emph{also} acquire hyperlinks: this is OK.

% This command tells LaTeX how to format your references in the biblography. The standard plain formatting, with
% references appearing in the order they are cited, is absolutely fine for our needs.